Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Related work finished

\noindent
\textbf{Algorithmic challenges.}
\maciek{Integer partition in non-augmented problem. Also: what to evict, rent or buy etc.}

@@

The studied model is related to online
paging~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}, sometimes also referred to
as online caching, where requests for data items (nodes) arrive over time and
need to be served from a cache of finite capacity, and where the number of
cache misses must be minimized. Classic problem variants usually boil down to
finding a smart eviction strategy, such as Least Recently Used (LRU)~\cite{SleTar85}. In our
setting, requests can be served remotely (i.e.,~without fetching the
corresponding nodes to a single physical machine). In this light, our model is more
reminiscent of caching models \emph{with
bypassing}~\cite{EpImLN11,EpImLN15,Irani02}.
A major difference between  these problems is that in the caching problems, each request involves a~single element of the universe, while in our model \emph{both} endpoints of a communication request are subject to~optimization.

@@

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The first three rows show the results for the general partitioning model, and last row shows the results for the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}

>>>>

@@

Our problem is further related to some classic online problems.
In particular, it is related to online paging~\cite{SleTar85,FKLMSY91,McGSle91,AcChNo00}, sometimes also referred to
as online caching, where requests for data items (nodes) arrive over time and
need to be served from a cache of finite capacity, and where the number of
cache misses must be minimized. Classic problem variants usually boil down to
finding a smart eviction strategy, such as Least Recently Used (LRU)~\cite{SleTar85}. In our
setting, requests can be served remotely (i.e.,~without fetching the
corresponding nodes to a single physical machine). In this light, our model is more
reminiscent of caching models \emph{with
bypassing}~\cite{EpImLN11,EpImLN15,Irani02}.
A major difference between  these problems is that in the caching problems, each request involves a~single element of the universe, while in our model \emph{both} endpoints of a communication request are subject to~optimization.
In this light, we can see our model as a "symmetric" version of online paging.

Dynamic graph partitioning problems are generally fundamental in computer science, and arise in many different contexts \cite{streaming-soda,streaming1}.

@@

\begin{table*}
	\centering
	\renewcommand{\arraystretch}{1.5}
	\begin{tabular}{>{\centering\arraybackslash}p{4.5cm}|>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{4.5cm}}
		\rowcolor{gray!50}
		\textbf{Variant} & \textbf{ Lower bound} &\textbf{Upper bound}\\ \hline 
		\textbf{$k=2$}& 3\hspace{0.3cm}\cite{repartition-disc} & 6\hspace{0.3cm}(\S \ref{sec:k2}) \\ 
		\rowcolor{gray!25}
		\textbf{$k=3$}&  $\Omega(\ell)$ \hspace{0.3cm}(\S \ref{sec:lowerbound})& $O(\ell) $\hspace{0.3cm}(\S \ref{sec:k3})\\
		$k > 3$ & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k^2 \cdot \ell^2)$\hspace{0.1cm} \cite{repartition-disc} \\
		\rowcolor{gray!25}
		Learning model & $\Omega(k\cdot \ell)$\hspace{0.3cm}(\S  \ref{sec:lowerbound})&$O(k \cdot \ell)$\hspace{0.3cm} (\S \ref{sec:ppl}) \\
	\end{tabular}
	\caption{Overview of known results and the results provided in this paper. By $\Rep$ we denote the cost of a single component repartition, and we elaborate on this in Section~\ref{sec:k3}. The first three rows show the results for the general partitioning model, except for the last row that shows the results for the learning model for arbitrary $k$ and $\ell$.
	}
	\label{tab:overview}
	\vspace{-7mm}
\end{table*}
